Miniproject - Analytic Number Theory

### 2021-12-07 Analytic number theory/submission.tex
Added part III (vi) to ant and fixed some minor points in all miniprojects

    To show surjectivity, consider some Dirichlet character $\chi: \N \to \C$ and construct a group homomorphism $f: (\Z/q\Z)^\units \to \C^\units$. 
    For each $x \in (\Z/q\Z)^\units$, there is a representative $n \in \N$ of $x$ and as $\chi(n)$ does not depend on the choice of $n$, we may define $f(x) := \chi(n)$.
    Note that as $x \in (\Z/q\Z)^\units$, we find $n \perp q$ and so $\chi(n) \neq 0$, i.e. $\chi(n) \in \C^*$.
    Then clearly for $a, b \in (\Z/q\Z)^*$ with representatives $n, m \in \N$ have
    \begin{equation*}
        f(ab) = \chi(nm) = \chi(n)\chi(m) = f(a)f(b)
    \end{equation*}
    So $f$ is a well-defined group homomorphism and we obviously have $\chi_f = \chi$.
\end{proof}
For simplicity of notation we sometimes will identify a Dirichlet character and its group homomorphism if it is always clear which one is meant.
\begin{example}[Ex (i)]
    \label{ex:nontrivial_dirichlet_character_mod_4}
    The function
    \begin{equation*}
        f: \N \to \C, \quad n \mapsto \begin{cases}
            0 & \text{if $n \equiv 0, 2 \mod 4$} \\
            1 & \text{if $n \equiv 1 \mod 4$} \\
            -1 & \text{if $n \equiv 3 \mod 4$}
        \end{cases}
    \end{equation*}
    is a Dirichlet character.
\end{example}
\begin{proof}
    This follows directly from Lemma~\ref{prop:characterization_dirichlet_character}, as $f = \chi_g$ for the group homomorphism
    \begin{equation*}
        g: (\Z/4\Z)^\units = \{ 1, 3 \} \to \C^*, \quad 1 \mapsto 1, \ 3 \mapsto -1
    \end{equation*}
    (this is a group homomorphism, as $3^2 = 9 \equiv 1 \mod 4$)
\end{proof}
Now we want to define Dirichlet series of Dirichlet characters.
\begin{proposition}
    For a Dirichlet character $\chi: \N \to \C$ and some $\epsilon > 0$, the series
    \begin{equation*}
        L(s, f) := \sum_{n \geq 1} f(n) n^{-s}
    \end{equation*}
    converges uniformly on $\Re(s) \geq 1 + \epsilon$.
    We will call it the Dirichlet series of $\chi$.
\end{proposition}
\begin{proof}
    By Lemma~\ref{prop:characterization_dirichlet_character}, we know that $\chi$ corresponds to a group homomorphism $f: (\Z/q\Z)^\units \to \C^\units$ such that $\chi(\N) = f((\Z/q\Z)^*) \cup \{ 0 \} \subseteq \C$ is a finite subset of $\C$.
    Hence, there is $C > 0$ with $|\chi(n)| \leq C$ for all $n \in \N$, and it follows that
    \begin{equation*}
        \sum_{1 \leq n \leq X} \left| \chi(n) n^{-s} \right| \leq \sum_{1 \leq n \leq X} C \left| n^{-s} \right| \leq C \sum_{1 \leq n \leq X} n^{-1 - \epsilon} \leq C \sum_{n \geq 1} n^{-1 - \epsilon}
    \end{equation*}
    which is finite.
\end{proof}
\begin{proposition}
    \label{prop:dirichlet_series_at_one}
    Let $f: (\Z/q\Z)^\units \to \C^\units$ be a group homomorphism. Then for the associated Dirichlet character $\chi = \chi_f$ we have that
    \begin{equation*}
        \lim_{s \to 1^+} L(s, \chi) \ \text{exists} \ \Leftrightarrow \ \sum_{x \in (\Z/q\Z)^\units} f(x) = 0
    \end{equation*}
    If this is the case, then
    \begin{equation*}
        \lim_{s \to 1} L(s, \chi) = \sum_{n \geq 1} \frac {\chi(n)} n
    \end{equation*}
    where the right-hand side converges (but not absolutely).
\end{proposition}
\begin{proof}
    Let $c = \sum_{x \in (\Z/q\Z)^\units} f(x)$.
    For the direction $\Rightarrow$ assume that $c \neq 0$.
    Then have for $\Re(s) > 1$ that
    \begin{align*}
        \sgn(c) \sum_{n \geq 1} \chi(n) n^{-s} &= \sum_{n \geq 0} \ \sum_{0 < k \leq q} \sgn(c) \chi(qn + k) (qn + k)^{-s} \\
        &\geq \sum_{n \geq 0} \ \sum_{0 < k \leq q}\sgn(c) \chi(qn + k) (qn + n)^{-s} \\
        &= \sum_{n \geq 0} \sgn(c) (qn + n)^{-s} \underbrace{\sum_{0 < k \leq q} \chi(qn + k)}_{= c} \\
        &\geq \frac {|c|} {(q + 1)^s} \sum_{n \geq 1} n^{-s} = \frac {|c|} {(q + 1)^s} \zeta(s)
    \end{align*}
    which clearly has a pole at $s = 1$. Hence $\lim_{s \to 1^+} L(s, \chi_f)$ cannot exist.

@@

@@

    It follows that $\lim_{t \to s} L(t, \chi_f)$ exists and is equal to $\sum_{n \geq 1} \chi(n) n^{-s}$.

@@

    For the last part, note that for any $q$-th root of unity $\xi$, we have $\xi\overline{\xi} \in \R$ with $\xi\overline{\xi} = |\xi|^2 > 0$.
    Furthermore, $\overline{\xi}$ is also a $q$-th root of unity, and so we see that $\xi\overline{\xi} = 1$ (the only real, positive root of unity is 1).
    It follows that for any Dirichlet character $\chi$ have $\overline{\chi([a])} = \chi([a]^{-1})$.
    Thus
    \begin{equation*}
        \sum_{\chi \in \mathrm{Dir}(q)} \chi(a)\overline{\chi(b)} = \sum_{\chi \in \mathrm{Dir}(q)} \chi([a][b]^{-1}) = \begin{cases}
            q - 1 & \text{if $[a][b]^{-1} = 1 \in (\Z/q\Z)^\units$} \\
            0 & \text{otherwise}
        \end{cases}
    \end{equation*}
    The condition $ab^{-1} = 1$ is equivalent to $a \equiv b \mod q$, so the claim follows.
\end{proof}
Using these basic results, we can now prove facts on the Dirichlet series of characters.
\begin{proposition}[Ex (iv)]
    \label{prop:representation_mangoldt_series_congruent_a}
    Let $a \perp q$. Then for $\Re(s) > 1$ have
    \begin{equation*}
        \sum_{n \equiv a \mod q} \frac {\Lambda(n)} {n^s} = \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s}
    \end{equation*}
    (All those series obviously converge absolutely since $\Re(s) > 1$)
\end{proposition}
\begin{proof}
    By Prop.~\ref{prop:finite_sums_characters} we have for all $n \in \N$ that
    \begin{equation*}
        \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \chi(n) = \begin{cases}
            1 & \text{if $a \equiv n \mod q$} \\
            0 & \text{otherwise}
        \end{cases}
    \end{equation*}
    It follows that
    \begin{align*}
        \sum_{n \equiv a \mod q} \Lambda(n) n^{-s} =& \sum_{n \geq 1} \Lambda(n) n^{-s} \begin{cases}
            1 & \text{if $a \equiv n \mod q$} \\
            0 & \text{otherwise}
        \end{cases} \\
        =& \sum_{n \geq 1} \Lambda(n) n^{-s} \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \chi(n) \\
        =& \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \Lambda(n) \chi(n) n^{-s} 
    \end{align*}
    as infinite summation clearly commutes with finite sums.
\end{proof}
\begin{example}[Ex (v)]
    We consider the Dirichlet characters mod 5.
    A (primitive) 5-th root of unity $\omega_5 \in \C$ is given by $\omega_5 = \exp(2\pi i/5)$.
    On the other hand, a primitive root modulo 5 is e.g. given by $r = 2$ since $2^2 \equiv -1 \mod 5$.
    Thus we have $5 - 1 = 4$ Dirichlet characters mod 5, namely those given by
    \begin{align*}
        1 &\mapsto 1,\ 2 \mapsto \omega_5 = \exp(2\pi i/5),\ 3 \mapsto \omega_5^3 = \exp(6\pi i/5),\ 4 \mapsto \omega_5^2 = \exp(4\pi i/5),\ \\
        1 &\mapsto 1,\ 2 \mapsto \omega_5^2 = \exp(4\pi i/5),\ 3 \mapsto \omega_5 = \exp(2\pi i/5),\ 4 \mapsto \omega_5^4 = \exp(8\pi i/5),\ \\
        1 &\mapsto 1,\ 2 \mapsto \omega_5^3 = \exp(6\pi i/5),\ 3 \mapsto \omega_5^4 = \exp(8\pi i/5),\ 4 \mapsto \omega_5^1 = \exp(2\pi i/5),\ \\
        1 &\mapsto 1,\ 2 \mapsto \omega_5^4 = \exp(8\pi i/5),\ 3 \mapsto \omega_5^2 = \exp(4\pi i/5),\ 4 \mapsto \omega_5^3 = \exp(6\pi i/5),\ \\
    \end{align*}
\end{example}

@@

    By Prop.~\ref{prop:representation_mangoldt_series_congruent_a} we have that for $\Re(s) > 1$
    \begin{equation*}
        \rho_a(s) = \sum_{n \equiv a \mod q} \Lambda(n) n^{-s}
    \end{equation*}
    Partial summation yields that for $\Re(s) > 1$ have
    \begin{align*}
        \rho_a(s) =& \sum_{n \equiv a \mod q} \Lambda(n) n^{-s} \\
        =& \lim_{t \to \infty} \Bigl( \underbrace{ t^{-s} \sum_{n < t, \ n \equiv a \mod q} \Lambda(n) }_{ = t^{-s} \Psi_a(t) = t^{-s} O(t\log t) = o(1)} \Bigr) 
        + s \int_1^\infty \Bigl( \underbrace{\sum_{n < t, \ n \equiv a \mod q} \Lambda(n) }_{ = \Psi_a(t)} \Bigr) t^{-(s + 1)} dt \\
        =& s \int_1^\infty \Psi_a(t) t^{-s - 1} dt = s \int_1^\infty O(t^{1/2}\log t) t^{-s - 1} dt \\
        =& O\left( |s| \int_1^\infty \log(t) t^{-\Re(s) - 1/2} dt \right) \\
        =& O\left( |s| \left( \frac 1 {1/2 - \Re(s)} 1^{1/2 - \Re(s)} + \frac 1 {1/2 - \Re(s)} \int_1^\infty t^{-\Re(s) - 1/2} dt \right) \right) \\
        =& O\left( |s| \frac 1 {(1/2 - \Re(s))^2} \right)
    \end{align*}
    However this function has no pole at $s = 1$, a contradiction to Lemma~\ref{prop:rho_pole_at_one}.
\end{proof}

>>>>

    To show surjectivity, consider some Dirichlet character $\chi: \N \to \C$ and construct a group homomorphism $f: (\Z/q\Z)^\units \to \C^\units$. 
    For each $x \in (\Z/q\Z)^\units$, there is a representative $n \in \N$ of $x$ and as $\chi(n)$ does not depend on the choice of $n$, we may define $f(x) := \chi(n)$.
    Note that as $x \in (\Z/q\Z)^\units$, we find $n \perp q$ and so $\chi(n) \neq 0$, i.e. $\chi(n) \in \C^*$.
    Then clearly for $a, b \in (\Z/q\Z)^*$ with representatives $n, m \in \N$ have
    \begin{equation*}
        f(ab) = \chi(nm) = \chi(n)\chi(m) = f(a)f(b)
    \end{equation*}
    So $f$ is a well-defined group homomorphism and we obviously have $\chi_f = \chi$.
\end{proof}
For simplicity of notation we sometimes will identify a Dirichlet character and its group homomorphism if it is always clear which one is meant.
\begin{example}[Ex (i)]
    \label{ex:nontrivial_dirichlet_character_mod_4}
    The function
    \begin{equation*}
        f: \N \to \C, \quad n \mapsto \begin{cases}
            0 & \text{if $n \equiv 0, 2 \mod 4$} \\
            1 & \text{if $n \equiv 1 \mod 4$} \\
            -1 & \text{if $n \equiv 3 \mod 4$}
        \end{cases}
    \end{equation*}
    is a Dirichlet character.
\end{example}
\begin{proof}
    This follows directly from Lemma~\ref{prop:characterization_dirichlet_character}, as $f = \chi_g$ for the group homomorphism
    \begin{equation*}
        g: (\Z/4\Z)^\units = \{ 1, 3 \} \to \C^*, \quad 1 \mapsto 1, \ 3 \mapsto -1
    \end{equation*}
    (this is a group homomorphism, as $3^2 = 9 \equiv 1 \mod 4$)
\end{proof}
Now we want to define Dirichlet series of Dirichlet characters.
\begin{proposition}
    For a Dirichlet character $\chi: \N \to \C$ and some $\epsilon > 0$, the series
    \begin{equation*}
        L(s, \chi) := \sum_{n \geq 1} \chi(n) n^{-s}
    \end{equation*}
    converges uniformly on $\Re(s) \geq 1 + \epsilon$.
    We will call it the Dirichlet series of $\chi$.
\end{proposition}
\begin{proof}
    By Lemma~\ref{prop:characterization_dirichlet_character}, we know that $\chi$ corresponds to a group homomorphism $f: (\Z/q\Z)^\units \to \C^\units$ such that $\chi(\N) = f((\Z/q\Z)^*) \cup \{ 0 \} \subseteq \C$ is a finite subset of $\C$.
    Hence, there is $C > 0$ with $|\chi(n)| \leq C$ for all $n \in \N$, and it follows that
    \begin{equation*}
        \sum_{1 \leq n \leq X} \left| \chi(n) n^{-s} \right| \leq \sum_{1 \leq n \leq X} C \left| n^{-s} \right| \leq C \sum_{1 \leq n \leq X} n^{-1 - \epsilon} \leq C \sum_{n \geq 1} n^{-1 - \epsilon}
    \end{equation*}
    which is finite.
\end{proof}
\begin{proposition}
    \label{prop:dirichlet_series_at_one}
    Let $f: (\Z/q\Z)^\units \to \C^\units$ be a group homomorphism. Then for the associated Dirichlet character $\chi = \chi_f$ we have that
    \begin{equation*}
        \lim_{s \to 1^+} L(s, \chi) \ \text{exists} \ \Leftrightarrow \ \sum_{x \in (\Z/q\Z)^\units} f(x) = 0
    \end{equation*}
    If this is the case, then
    \begin{equation*}
        \lim_{s \to 1^+} L(s, \chi) = \sum_{n \geq 1} \frac {\chi(n)} n
    \end{equation*}
    where the right-hand side converges (but not absolutely).
\end{proposition}
\begin{proof}
    Let $c = \sum_{x \in (\Z/q\Z)^\units} f(x)$.
    For the direction $\Rightarrow$ assume that $c \neq 0$.
    Then have for $\Re(s) > 1$ that
    \begin{align*}
        \sgn(c) \sum_{n \geq 1} \chi(n) n^{-s} &= \sum_{n \geq 0} \ \sum_{0 < k \leq q} \sgn(c) \chi(qn + k) (qn + k)^{-s} \\
        &\geq \sum_{n \geq 0} \ \sum_{0 < k \leq q}\sgn(c) \chi(qn + k) (qn + n)^{-s} \\
        &= \sum_{n \geq 0} \sgn(c) (qn + n)^{-s} \underbrace{\sum_{0 < k \leq q} \chi(qn + k)}_{= c} \\
        &\geq \frac {|c|} {(q + 1)^s} \sum_{n \geq 1} n^{-s} = \frac {|c|} {(q + 1)^s} \zeta(s)
    \end{align*}
    which clearly has a pole at $s = 1$. Hence $\lim_{s \to 1^+} L(s, \chi_f)$ cannot exist.

@@

    We will only consider real $s$ now.

@@

    It follows that $\lim_{t \to s^+} L(t, \chi_f)$ exists and is equal to $\sum_{n \geq 1} \chi(n) n^{-s}$.

@@

    For the last part, note that for any $q$-th root of unity $\xi$, we have $\xi\overline{\xi} \in \R$ with $\xi\overline{\xi} = |\xi|^2 > 0$.
    Furthermore, $\overline{\xi}$ is also a $q$-th root of unity, and so we see that $\xi\overline{\xi} = 1$ (the only real, positive root of unity is 1).
    It follows that for any Dirichlet character $\chi$ have $\overline{\chi([a])} = \chi([a]^{-1})$.
    Thus
    \begin{equation*}
        \sum_{\chi \in \mathrm{Dir}(q)} \chi(a)\overline{\chi(b)} = \sum_{\chi \in \mathrm{Dir}(q)} \chi([a][b]^{-1}) = \begin{cases}
            q - 1 & \text{if $[a][b]^{-1} = 1 \in (\Z/q\Z)^\units$} \\
            0 & \text{otherwise}
        \end{cases}
    \end{equation*}
    The condition $ab^{-1} = 1$ is equivalent to $a \equiv b \mod q$, so the claim follows.
\end{proof}
Using these basic results, we can now prove facts on the Dirichlet series of characters.
\begin{proposition}[Ex (iv)]
    \label{prop:representation_mangoldt_series_congruent_a}
    Let $a \perp q$. Then for $\Re(s) > 1$ have
    \begin{equation*}
        \sum_{n \equiv a \mod q} \frac {\Lambda(n)} {n^s} = \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s}
    \end{equation*}
    (All those series obviously converge absolutely since $\Re(s) > 1$)
\end{proposition}
\begin{proof}
    By Prop.~\ref{prop:finite_sums_characters} we have for all $n \in \N$ that
    \begin{equation*}
        \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \chi(n) = \begin{cases}
            1 & \text{if $a \equiv n \mod q$} \\
            0 & \text{otherwise}
        \end{cases}
    \end{equation*}
    It follows that
    \begin{align*}
        \sum_{n \equiv a \mod q} \Lambda(n) n^{-s} =& \sum_{n \geq 1} \Lambda(n) n^{-s} \begin{cases}
            1 & \text{if $a \equiv n \mod q$} \\
            0 & \text{otherwise}
        \end{cases} \\
        =& \sum_{n \geq 1} \Lambda(n) n^{-s} \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \chi(n) \\
        =& \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \Lambda(n) \chi(n) n^{-s} 
    \end{align*}
    as infinite summation clearly commutes with finite sums.
\end{proof}
\begin{example}[Ex (v)]
    \label{ex:nontrivial_dirichlet_characters_mod_5}
    We consider the Dirichlet characters mod 5.
    A (primitive) 5-th root of unity $\omega_5 \in \C$ is given by $\omega_5 = \exp(2\pi i/5)$.
    On the other hand, a primitive root modulo 5 is e.g. given by $r = 2$ since $2^2 \equiv -1 \mod 5$.
    Thus we have the trivial Dirichlet character $\chi_0$ and $5 - 1 = 4$ nontrivial Dirichlet characters mod 5, namely those given by
    \begin{align*}
        \chi_1: 1 &\mapsto 1,\ 2 \mapsto \omega_5 = \exp(2\pi i/5),\ 3 \mapsto \omega_5^3 = \exp(6\pi i/5),\ 4 \mapsto \omega_5^2 = \exp(4\pi i/5),\ \\
        \chi_2: 1 &\mapsto 1,\ 2 \mapsto \omega_5^2 = \exp(4\pi i/5),\ 3 \mapsto \omega_5 = \exp(2\pi i/5),\ 4 \mapsto \omega_5^4 = \exp(8\pi i/5),\ \\
        \chi_3: 1 &\mapsto 1,\ 2 \mapsto \omega_5^3 = \exp(6\pi i/5),\ 3 \mapsto \omega_5^4 = \exp(8\pi i/5),\ 4 \mapsto \omega_5^1 = \exp(2\pi i/5),\ \\
        \chi_4: 1 &\mapsto 1,\ 2 \mapsto \omega_5^4 = \exp(8\pi i/5),\ 3 \mapsto \omega_5^2 = \exp(4\pi i/5),\ 4 \mapsto \omega_5^3 = \exp(6\pi i/5),\ \\
    \end{align*}
\end{example}

@@

    By Prop.~\ref{prop:representation_mangoldt_series_congruent_a} we have that for $\Re(s) > 1$
    \begin{equation*}
        \rho_a(s) = \sum_{n \equiv a \mod q} \Lambda(n) n^{-s}
    \end{equation*}
    Partial summation yields that for $\Re(s) > 1$ have
    \begin{align*}
        \rho_a(s) =& \sum_{n \equiv a \mod q} \Lambda(n) n^{-s} \\
        =& \lim_{t \to \infty} \Bigl( \underbrace{ t^{-s} \sum_{n < t, \ n \equiv a \mod q} \Lambda(n) }_{ = t^{-s} \Psi_a(t) = t^{-s} O(t\log t) = o(1)} \Bigr) 
        + s \int_1^\infty \Bigl( \underbrace{\sum_{n < t, \ n \equiv a \mod q} \Lambda(n) }_{ = \Psi_a(t)} \Bigr) t^{-(s + 1)} dt \\
        =& s \int_1^\infty \Psi_a(t) t^{-s - 1} dt = s \int_1^\infty O(t^{1/2}\log t) t^{-s - 1} dt \\
        =& O\left( |s| \int_1^\infty \log(t) t^{-\Re(s) - 1/2} dt \right) \\
        =& O\left( |s| \left( \frac 1 {1/2 - \Re(s)} 1^{1/2 - \Re(s)} + \frac 1 {1/2 - \Re(s)} \int_1^\infty t^{-\Re(s) - 1/2} dt \right) \right) \\
        =& O\left( |s| \frac 1 {(1/2 - \Re(s))^2} \right)
    \end{align*}
    However this function has no pole at $s = 1$, a contradiction to Lemma~\ref{prop:rho_pole_at_one}.
\end{proof}
\begin{example}[Ex (vi)]
    For all the nontrivial Dirichlet characters $\chi_1, ..., \chi_4$ defined in Example~\ref{ex:nontrivial_dirichlet_characters_mod_5}, we have
    \begin{equation*}
        L(1, \chi_i) \neq 0
    \end{equation*}
    It follows that there are infinitely many primes $\equiv a \mod 5$, for all $a \perp 5$.
\end{example}
\begin{proof}
    By Prop.~\ref{prop:dirichlet_series_at_one} we know that
    \begin{equation*}
        L(1, \chi_i) = \sum_{n \geq 1} \chi(n) n^{-s}
    \end{equation*}
    For the fifth root of unity $\omega \in \C$ such that $\chi_i(1) = \omega$, we thus find
    \begin{align*}
        L(1, \chi_i) =& \sum_{k \geq 0} \sum_{1 \leq n \leq 4} \frac {\chi(5k + n)} {(5k + n)^s} = \sum_{k \geq 0} \frac {\omega} {(5k + 1)^s} + \frac {\omega^2} {(5k + 2)^s} + \frac {\omega^3} {(5k + 3)^s} + \frac {\omega^4} {(5k + 4)^s} \\
        =& \sum_{k \geq 0} \omega \Bigl( \underbrace{\frac 1 {(5k + 1)^s} - \frac 1 {(5k + 4)^s}}_{> 0} \Bigr) + \omega^2 \Bigl( \underbrace{\frac 1 {(5k + 2)^s} - \frac 1 {(5k + 3)^s}}_{> 0} \Bigr)
    \end{align*}
    Hence we have positive coefficients $a_k, b_k > 0$ with
    \begin{equation*}
        L(1, \chi_i) - \sum_{k \geq 0} a_k \omega + b_k \omega^2 = \omega \sum_{k \geq 0} a_k + b_k \omega
    \end{equation*}
    In particular,
    \begin{equation*}
        \Im\left( \frac {L(1, \chi_i)} {\omega} \right) = \sum_{k \geq 0} b_k \Im(\omega) = \Im(\omega) \underbrace{ \sum_{k \geq 0} b_k }_{> 0}
    \end{equation*}
    Since $\chi_i$ is a nontrivial Dirichlet character, we see that $\Im(\omega) \neq 0$ and so $\Im(L(1, \chi_i)/\omega) \neq 0$, thus $L(1, \chi_i) \neq 0$.
\end{proof}
\begin{remark}[Ex (vii)]
    TODO
\end{remark}
